---
title: "An practical Examination of Ticket Sales and Redemption Trends: Awareness from Toronto Island Ferry Data"
author:
  - Xinrui Xie
thanks: "A GitHub Repository containing all data, R code, and other files used in this investigation is located here: <https://github.com/bennyrochwerg/healthcare-outbreaks-toronto>"
date: 09-23-2024
date-format: long
abstract: "Ferries to Toronto Island Park operate year-round out of Jack Layton Ferry Terminal. Ferries carry passengers to and from Centre Island, Hanlan’s Point and Ward’s Island. There are limited amenities during the off-season. This dataset provides near real-time information on ferry ticket sales and ticket redemptions. The counts are provided in 15 minute intervals and are updated hourly. They encompass all product types and include both online and POS-kiosk sales.
For additional information about Toronto Island Park or the ferry service, please visit toronto.ca/parks or contact parks@toronto.ca."
format: pdf
number-sections: true
# The toc parameter used to create a table of contents was obtained from
# Quarto documentation:
# https://quarto.org/docs/reference/formats/pdf.html
toc: true
bibliography: references.bib
---

```{r}
#| echo: false
#| warning: false
#### Preamble ####

# Purpose: 
# Author: 
# Date: September 23, 2024
# Contact: 
# Pre-requisites: Run the files "01-download_data.R" and "02-data_cleaning.R".
```

```{r}
#| echo: false
#| warning: false
#### Loading Packages ####

# install.packages("tidyverse")
# install.packages("here")
library(tidyverse)
library(here)
library(opendatatoronto)
library(tidyverse)
```

# Introduction {#sec-introduction}
The purpose of this study is to analyze Toronto Island Ferry ticketing data using various statistical methods. With this this study attempts to reveal and express notable trends and insights that may inform decisions related to, for example, the opening times of large rides. The data provides valuable insights into the tourism and entertainment industry, as well as the leisure services industry, and is presented in visualizations that allow for a deeper understanding.

# Data {#sec-data}

## Overview {#sec-data-overview}
The dataset used in this study contains near real-time information on the total number of ferry ticket sales and ticket exchanges over a defined period of time. The analysis used R statistical software to generate a variety of graphs, including histograms, bar charts, and line graphs, which are essential for understanding the distribution and relationships of key variables. The main objective of the study was to explore which ticketing method had the highest sales over time.

## Results {#sec-data-results}

```{r}
#| echo: false
#| warning: false
#| message: false

#### Loading the Cleaned Dataset ####
ferry_ticket_packages <- search_packages("Toronto Island Ferry Ticket Counts")
ferry_ticket_packages
# Retrieve a list of all resources (datasets) available within the found package
ferry_ticket_resources <- ferry_ticket_packages %>%
  list_package_resources()
# Display the list of resources available in the "Marriage Licence Statistics" package
ferry_ticket_resources

ferry_ticket_statistics <- ferry_ticket_resources[2,] %>%
  get_resource()

data = ferry_ticket_statistics
```

\newpage

```{r}
#| echo: false
#| warning: false

#### First Graph Labels ####

# This code is based on knowledge from STA304 (2024).


```

```{r}
#| echo: false
#| warning: false
#| label: fig-box-plot-of-counts
#| fig-cap: ""

#### First Graph ####

# This code is based on knowledge from STA304 (2024).

# Box plot for Redemption.Count and Sales.Count
ggplot(data, aes(x = factor(1), y = Redemption.Count)) +
  geom_boxplot(fill = "blue") +
  labs(x = '', y = 'Redemption Count')

ggplot(data, aes(x = factor(1), y = Sales.Count)) +
  geom_boxplot(fill = "red") +
  labs(title = 'Box Plot of Sales Count', x = '', y = 'Sales Count')


```



\newpage

```{r}
#| echo: false
#| warning: false

#### Second Graph Labels ####

# This code is based on knowledge from STA304 (2024).

```

```{r}
#| echo: false
#| warning: false
#| label: fig-Scatter-plot-between-Redemption.Count-and- Sales.Count
#| fig-cap: ""

#### Second Graph ####

# This code is based on knowledge from STA304 (2024).

# Scatter plot between Redemption.Count and Sales.Count
ggplot(data, aes(x = Sales.Count, y = Redemption.Count)) +
  geom_point(color = "green") +
  labs(title = 'Scatter Plot of Sales Count vs Redemption Count', x = 'Sales Count', y = 'Redemption Count')
```


\newpage

```{r}
#| echo: false
#| warning: false

#### Third Graph Labels ####

# This code is based on knowledge from STA304 (2024).

```

```{r}
#| echo: false
#| warning: false
#| label: fig-Bar-Plot-of-Redemption-and-sales-Count-Over-Time
#| fig-cap: " "

#### Third Graph ####

# This code is based on knowledge from STA304 (2024).
# Convert Timestamp to Date-Time format
data$Timestamp <- as.POSIXct(data$Timestamp, format="%Y-%m-%dT%H:%M:%S")

# Reshape the data for plotting
library(reshape2)
df_long <- melt(data, id.vars = "Timestamp", measure.vars = c("Redemption.Count", "Sales.Count"))

# Create a bar plot
ggplot(df_long, aes(x = Timestamp, y = value, fill = variable)) +
  geom_bar(stat = 'identity', position = 'dodge') +
  labs(title = 'Bar Plot of Redemption and Sales Count Over Time', x = 'Timestamp', y = 'Count') +
  scale_fill_manual(values = c("blue", "red"))


```



# Discussion {#sec-discussion}

 
\newpage

\appendix

# Appendix {#sec-appendix}

## Dataset and Graph Sketches {#sec-appendix-sketches}



## Data Cleaning {#sec-appendix-cleaning}



## Attribution Statement {#sec-appendix-attribution}



\newpage

# References {#sec-references}